Locality and Computational Reliability of Linear Response Calculations for Molecular Systems

### 2019-01-23 Supplementary_material.tex
modification of suypplementary

We report the results of the excitation landscape for the $C_{60}$ and the Aflatoxin molecules. This analysis allows us to investigate the multi-threshold structure for systems with larger number of atoms and/or lower degrees of symmetry respect to the ones presented in the main text. The plots of Fig. \ref{exc-land} evidence that, in both the cases, the sector of localized excitations is very rich and extends well above the first ionization potential of the molecule. These results provide a further confirmation of the behavior already observed in the Table I.

The growth of the localized sector with the number of atoms of the molecule seems to be a general feature. It can simply explained by observing that bigger molecules behave as wider potential wells and possess a high number of localized Kohn-Sham (KS) orbitals that span a wide energy range. 
A numerical evidence in support of this argument is presented in Fig. \ref{dos}, where the DOS of the KS (bound) orbitals of the Aflatoxin and $CO$ molecules are directly compared.  
In a simplified two-levels picture, in which $\op V'=0$, the KS empty orbitals $\psi_a$ coincide with the excitation modes defined in eq. (17) and the associated energy is parametrized as $\Omega_a=\epsilon_a-\epsilon_p$. In this case to the increase of the energy range spanned by the localized orbitals it directly corresponds a richer sector of localized excitations.
When $\op V'$ is switched on the excitation modes are expressed as a combination of KS orbitals but the presence of a high number of localized orbitals allows for a rich sector of localized excitations, as confirmed by the results of Fig. \ref{exc-land}.

>>>>

We have investigated how the multi-threshold structure of the localized excitations might be put in relation with respect to
the number of atoms and/or the symmetry of the molecule. To this end, we have considered two case-studies, the carbon Fullerene, a highly symmetric structure made of 60 atoms, and the B1 Aflatoxin, depicted in Fig.~\ref{aflab1}, which has 35 atoms in a low-symmetric configuration.

The plots of Fig. \ref{exc-land} evidence that, in both cases, the sector of localized excitations is very rich and extends well above the first ionization potential of the molecule. These results provide a further confirmation of the behavior already observed in Table I.
\begin{figure}[h]
  \centering
  \includegraphics[width=0.4\textwidth]{AflaB1.eps}
    \caption{Equilibrium position of the Aflatoxin B1}
\label{aflab1}
\end{figure}

It may be noticed that the number of localized excitations, either below or above the first ionization potentials is much higher than
the one of Fig.~5 of the paper, in the case of the Benzene molecule. This holds also for the low-symmetry aflatoxin molecule.

The growth of the localized sector with the number of atoms of the molecule seems thus to be a general feature.
A simple interpretation of this fact may be provided by considering perturbatively the coupling term $\op V'=0$ in Eq.~19 of the paper.
Indeed, larger molecules behave possess a high number of localized Kohn-Sham (KS) orbitals that span a wide energy range.
A numerical evidence in support of this argument is presented in Fig. \ref{dos}, where the DOS of the KS (bound) orbitals of the Aflatoxin and $CO$ molecules are directly compared.
In a simplified two-levels picture, in which $\op V'=0$, the KS empty orbitals $\psi_a$ coincide with the excitation modes defined in eq. (17) and the associated energy is parametrized as $\Omega_a=\epsilon_a-\epsilon_p$. In this case to the increase of the energy range spanned by the localized orbitals it directly corresponds a richer sector of localized excitations.
When $\op V'$ is switched on the excitation modes are expressed as a combination of KS orbitals but the presence of a high number of localized orbitals allows for a rich sector of localized excitations, as confirmed by the results of Fig. \ref{exc-land}.
